---
title: "LinkedEarth - Neotoma P418 Use Case"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

Step 1: Create a polygon to search for our site.

```{r}
locpoly <- matrix(c(-70,-71,-71,-70,45,45,44,44),ncol=2,byrow = F)

```
Step 2: Convert array to GeoJSON FeatureCollection.

```{r}
#install.packages("geojson")
library(geojson)

poly <- geojson::polygon(paste0('{ "type": "Polygon", "coordinates": [[', "[",locpoly[1,1],", ",locpoly[1,2],"],", " [",locpoly[2,1],", ",locpoly[2,2],"],", " [",locpoly[3,1],", ",locpoly[3,2],"],", " [",locpoly[4,1],", ", locpoly[4,2],"],", " [",locpoly[1,1],", ", locpoly[1,2],']]] }'))

feature <- geojson::feature(poly)
feature_collection <- geojson::featurecollection(feature)
feature_collection_str <- geo_pretty(feature_collection)
```

Step 3: Set type of search for spatial search.

```{r}
search_type <- "spatial/search/object"
```

Step 4: Set the request domain URL for the geodex web service. Please see http://geodex.org/swagger-ui/ for a complete description of the web service call formats.

```{r}
domain_url <- "http://geodex.org/api/v1/"
request_url <- paste(domain_url, search_type, sep="")
```

Step 5: Create an R list data structure to hold URL submission parameters

```{r}
params_list <- list(geowithin = feature_collection_str)
```

Step 6: Make call to the Geodex RESTful web service using the requests package.

```{r}
library(httr)
r <- GET(request_url, query = params_list)
results <- content(r, "text", encoding = "ISO-8859-1")
```

Step 7: Expore results.

```{r}
library(rjson)
results_json <- fromJSON(results)
features <- results_json$features
number_of_results <- length(features)
first_result <- features[[1]]

url <- first_result$properties$URL

```

Sort results by distance to polygon
```{r}

library(geosphere)
#find nearest coord in each feature
nearestInFeature <- function(feat){
  if(is.list(feat$geometry$coordinates)){
    coords <- matrix(unlist((feat$geometry$coordinates)),ncol=2,byrow = T)
  }else{
    coords <- matrix((feat$geometry$coordinates),ncol=2,byrow = T)
  }
  md =try(min(geosphere::distGeo(coords,locpoly[1,])))
  if(is.numeric(md)){
    return(md)
  }else{
      return(NA)
    }

}
nearestDist <- sapply(results_json$features,nearestInFeature)

#sort by nearest
results_json$features <- results_json$features[order(nearestDist)]



allUrls <- sapply(results_json$features,FUN = function(x){x$properties$URL})
geometry <- first_result$geometry$type
coordinates <- first_result$geometry$coordinates[[1]]


#print first 10 results
print(allUrls[1:10])
```

Numbers 2 & 7 are what we're looking for.


Explore the metadata for the LinkedEarth result

```{r}
dataset_url <- allUrls[7]
```

Step 13: Set the web service call for extracting a set of metadata.

```{r}
search_type <- "graph/details"
```
Step 14: Create the URL for the RESTful web service call.

```{r}
domain_url <- "http://geodex.org/api/v1/"

request_url <- paste(domain_url, search_type, sep="")
```

Step 15: Create the GET parameter for this call.

```{r}
params_list <- list(r = dataset_url)
```

Step 16: Execute the RESTful web service call.

```{r}
r <- GET(request_url, query = params_list)
results <- content(r, "text", encoding = "ISO-8859-1")
```

Step 17: Print the results in a user friendly way.

```{r}
results_json <- fromJSON(results)
print(paste("URI =", results_json$S))
print(paste("Alternate Name =", results_json$Aname))
print(paste("Name =", results_json$Name))
print(paste("URL =", results_json$URL))
print(paste("Description =", results_json$Description))
print(paste("Citation =", results_json$Citation))
print(paste("Data Published =", results_json$Datepublished))
print(paste("Dataset Download Link =", results_json$Curl))
print(paste("Keywords =", results_json$Keywords))
print(paste("License =", results_json$License))
```


Load in LinkedEarth LiPD 

```{r}
library(lipdR)
#L2 <- readLipd(allUrls[7])
L2 <- readLipd(results_json$Curl)
```


Explore the metadata for the Neotoma result

```{r}
dataset_url <- allUrls[2]
```

Step 15: Create the GET parameter for this call.

```{r}
params_list <- list(r = dataset_url)
```

Step 16: Execute the RESTful web service call.

```{r}
r <- GET(request_url, query = params_list)
results <- content(r, "text", encoding = "ISO-8859-1")
```

Step 17: Print the results in a user friendly way.

```{r}
results_json <- fromJSON(results)
print(paste("URI =", results_json$S))
print(paste("Alternate Name =", results_json$Aname))
print(paste("Name =", results_json$Name))
print(paste("URL =", results_json$URL))
print(paste("Description =", results_json$Description))
print(paste("Citation =", results_json$Citation))
print(paste("Data Published =", results_json$Datepublished))
print(paste("Dataset Download Link =", results_json$Curl))
print(paste("Keywords =", results_json$Keywords))
print(paste("License =", results_json$License))
```

Load in Neotoma file as a LiPD 

```{r}
library(geoChronR)
library(neotoma)
site = get_site("Basin Pond")
site2 = data.frame(site.id = 234)
L = neotoma2Lipd(site = site)
#estimate uncertainty from range
L$chronData[[2]]$measurementTable[[1]] = estimateUncertaintyFromRange(L$chronData[[2]]$measurementTable[[1]])
```

```{r}
detach("package:geojson",character.only = TRUE)
```




```{r,echo=FALSE}
L = runBacon(L,which.chron = 2,baconDir = "~/Dropbox/MacBacon/",modelNum = 2,
             remove.rejected = FALSE,labIDVar="chron.control.id", age14CVar = NULL, age14CuncertaintyVar = NULL, ageVar = "age",ageUncertaintyVar = "unc.estimate", depthVar = "depth", reservoirAge14CVar = NULL,reservoirAge14CUncertaintyVar = NULL,rejectedAgesVar=NULL,useMarine = FALSE,BaconAsk = FALSE, baconAccMean = 1,BaconSuggest = FALSE)
              
```



```{r}
plotChron(L,chron.number = 2,model.num = 2)
```


```{r}


L$paleoData[[1]]$measurementTable[[1]]$temperature <- L2$paleoData[[1]]$measurementTable[[1]]$temperature


L <- mapAgeEnsembleToPaleoData(L = L,which.chron = 2,which.paleo = 1,which.model = 2,which.ens = 1,which.pmt = 1,age.var = "ageEnsemble")
```
Now plot temperature with age uncertainty

```{r}
library(ggplot2)
temp <- selectData(L,"temperature")
ageEnsemble <- selectData(L,"ageEnsemble")

plot <- plotTimeseriesEnsRibbons(ageEnsemble,temp)
plot <- plotTimeseriesEnsLines(ageEnsemble,temp,color = "red",add.to.plot = plot,maxPlotN = 5)+
  scale_x_reverse("Age (yr BP)")
print(plot)
```

