---
title: "Geodex Spatial Search"
output:
  html_document:
    df_print: paged
---

Step 1: Create a variable for a spatial search location.

```{r}
location <- c(-90,40)
```

Step 2: Convert array to GeoJSON FeatureCollection.

```{r}
#install.packages("geojson")
library(geojson)

point <- geojson::point(paste('{ "type": "Point", "coordinates": [', location[1], ',' , location[2], '] }'))
feature <- geojson::feature(point)
feature_collection <- geojson::featurecollection(feature)
feature_collection_str <- geo_pretty(feature_collection)
```

Step 3: Set type of search for spatial search.

```{r}
search_type <- "spatial/search/object"
```

Step 4: Set the request domain URL for the geodex web service. Please see http://geodex.org/swagger-ui/ for a complete description of the web service call formats.

```{r}
domain_url <- "http://geodex.org/api/v1/"
request_url <- paste(domain_url, search_type, sep="")
```

Step 5: Create an R list data structure to hold URL submission parameters

```{r}
params_list <- list(geowithin = feature_collection_str)
```

Step 6: Make call to the Geodex RESTful web service using the requests package.

```{r}
library(httr)
r <- GET(request_url, query = params_list)
results <- content(r, "text", encoding = "ISO-8859-1")
```

Step 7: Expore results.

```{r}
library(rjson)
results_json <- fromJSON(results)
features <- results_json$features
number_of_results <- length(features)
first_result <- features[[1]]

url <- first_result$properties$URL
allUrls <- sapply(results_json$features,FUN = function(x){x$properties$URL})
geometry <- first_result$geometry$type
coordinates <- first_result$geometry$coordinates[[1]]

print(paste("Number of Results =", number_of_results))
print(paste("URL of First Result =", url))
print(paste("Coordinates of First Result = ", coordinates))
```

Step 8: Retrieve information about a selected URL resource.

```{r}
dataset_url <- "http://get.iedadata.org/doi/310660"
```

Step 9: Set the web service call for extracting a set of metadata.

```{r}
search_type <- "graph/details"
```

Step 10: Create the URL for the RESTful web service call.

```{r}
domain_url <- "http://geodex.org/api/v1/"
request_url <- paste(domain_url, search_type, sep="")
```

Step 11: Create the GET parameter for this call.

```{r}
params_list <- list(r = dataset_url)
```

Step 12: Execute the RESTful web service call.

```{r}
r <- GET(request_url, query = params_list)
results <- content(r, "text", encoding = "ISO-8859-1")
```

Step 13: Print the results in a user friendly way.

```{r}
results_json <- fromJSON(results)
print(paste("URI =", results_json$S))
print(paste("Alternate Name =", results_json$Aname))
print(paste("Name =", results_json$Name))
print(paste("URL =", results_json$URL))
print(paste("Description =", results_json$Description))
print(paste("Citation =", results_json$Citation))
print(paste("Data Published =", results_json$Datepublished))
print(paste("Dataset Download Link =", results_json$Curl))
print(paste("Keywords =", results_json$Keywords))
print(paste("License =", results_json$License))
```








